% !TEX TS-program = XeLaTeX

\documentclass[a4paper]{article}
\usepackage{fontspec}
\usepackage{cprotect}
\usepackage{color}
\usepackage[xetex,
            pdfauthor={moonblade168},
            pdftitle={Almanac},
            pdfsubject={},
            pdfkeywords={},
            pdfproducer={Oh, you checked the metadata?. Nice going. Here have a clue "cheatextends"},
            pdfcreator={}]{hyperref}
\pagecolor{white}
\pagenumbering{gobble}
\newcommand{\notch}[1]{\setmainfont{Bookman Old Styln}#1\setmainfont{Bookman Old Style}}
\newcommand{\row}{\vspace{5mm}}
\newcommand{\white}[1]{\textcolor{white}{\fontsize{1}{1.2}\selectfont{#1}}}
\setmainfont{Bookman Old Style}
\begin{document}
\begin{center}
\Large{\underline{The Almanac}}
\end{center}

\newenvironment{noSepEnumerate}
{ \begin{enumerate}
    \setlength{\itemsep}{1pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}}
{ \end{enumerate}}
First of all you're now an Egg Hunter, or for short, a Gunter. Congratulations.

\row
The almanac is going to be your bible, your rule book, your clue list and your best buddy for the hunt. The objective of the game is to find the Easter Egg. An ultimate race for glory riches and fame.

There are three keys of copper, jade and crystal, to unlock three gates. The gates stand between you and the Egg. Find the key, unlock the gates, grab the egg and you're the winner. A lot of obstacles stand in your way. Each key and gate will require patience and a brilliant mind to crack.

\row
\begin{centering}
Three hidden keys open three secret gates \\
Wherein the errant will be tested for worthy traits \\
And those with the skill to survive these straits \\
Will reach the end where the prize awaits \\
\end{centering}  

\row
\begin{flushleft}
Some Pointers
\end{flushleft}

\begin{noSepEnumerate}
	\item Commence your journey from the almanac
	\item Hard is the path that lies ahead of you, the weak will be eliminated
	\item Each key unlocks a gate, the gate doesn't budge without the key.
	\item Ab\notch{s}orb each line completely, Words and rhymes h\notch{a}ve power
	\item The hunt may feature ele\notch{m}ents from various games, treasure hunts, films and books; Being familiar with them gains you an edge
	\item Every inch of the almanac is im\notch{p}ortant, decode it entirely and you'll be ahead of everyone else
	\item Read the book Ready Player One to have some background on the game
	\item Pay attention to detail, for example, you should have noticed that the third pointer was the only one with a period at its end
	\item A textbox wi\notch{l}l only take in lower case letters, digits and symbols, no upper case or spaces
	\item Remember that hacks and ch\notch{e}ats don't work and may lead to a ban
	\item Tinyurl is awesome, it takes a bunch of letters with or without meaning and gives you a url
	\item Only I is important (pun intended), You are your own team
	\item Never hesitate to bend the rules
	\item Enjoy the game, but don't be that guy who ruins it for others by posting spoilers
\end{noSepEnumerate}

\white{\texttt{.. .-.. --- ...- . -.. .- -. -... .-. --- .-- -. --..-- ... - . .--. .... . -. ..-. .- .-.. -.- . -. --..-- .- -. -.. - --- .-.. -.- .. . -. .-.-.-}}
\end{document}

